Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
add section about the author

>>>>

\section{About the author}
Dieter Adriaenssens currently works at Ghent University and is a sysadmin since 2005. He is an active Open Source community member, who contributed to phpMyAdmin and other projects, regularly attending and speaking at conferences, like FOSDEM.\\
Recently, Dieter started exploring the world of Android application development, which resulted in a first release of a navigation app a few months ago.\\
He lives in Ghent, Belgium and enjoys rock climbing.
\begin{itemize}
  \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
  \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
\end{itemize}
